Index measures for oak decline severity using phenotypic descriptors

### 2019-12-17 manuscript/manuscript.Rmd
added to discussion

- Association of PDI and overall oak decline with crown condition well documented
- Association of crown condition and AOD severity. Could not previously be shown by @denman2014.
- Bleed prevalence and AOD
- Agrillus exit hole occurance with stem bleeding - smaller area surveyed compared to bleeding. Trees with bleeds do not always have stem bleeds [@brown2017a;@vansteenkiste2004]
- Size differences between AOD and COD trees

>>>>

- Association of PDI and overall oak decline with crown condition well documented
- Association of crown condition and AOD severity in trees  Could not previously be shown by @denman2014.
- Bleed prevalence and AOD

There was no contribution of *A. biguttatus* exit hole occurance with with the DAI and therefore stem bleeding - smaller area surveyed compared to bleeding. It has also been found previouly that trees with bleeds do not always have exit holes as  [@brown2017a;@vansteenkiste2004].

- Size differences between AOD and COD trees
